\begin{thebibliography}{1}
    \bibitem{bib1}
        \begin{latin}
            "NCBI BLAST Documentation," [Online].\\
            Available: https://blast.ncbi.nlm.nih.gov/Blast.cgi.
        \end{latin}

    \bibitem{bib2}
        \begin{latin}
            "Logomaker: beautiful sequence logos in Python," [Online]. \\
            Available: https://logomaker.readthedocs.io/. [Accessed: Feb. 5, 2025].
        \end{latin}

    \bibitem{bib3}
        \begin{latin}
            "Biopython: Python Tools for Computational Molecular Biology," [Online]. \\ Available: https://biopython.org/. [Accessed: Feb. 7, 2025].
        \end{latin}

    \bibitem{bib4}
        \begin{latin}
            "Position-specific scoring matrix," Wikipedia, The Free Encyclopedia. [Online]. \\
            Available: https://en.wikipedia.org/wiki/Position-specific\_scoring\_matrix. [Accessed: Feb. 7, 2025].
        \end{latin}

    \bibitem{bib5}
        \begin{latin}
             "Markov model," Wikipedia, The Free Encyclopedia. [Online]. \\
             Available: https://en.wikipedia.org/wiki/Markov\_model. [Accessed: Feb. 6, 2025].
        \end{latin}

    \bibitem{bib6}
        \begin{latin}
            "Sequence alignment," Wikipedia, The Free Encyclopedia. [Online]. \\
            Available: https://en.wikipedia.org/wiki/Sequence\_alignment. [Accessed: Feb. 6, 2025].
        \end{latin}

    \bibitem{bib7}
        \begin{latin}
            "PSI-BLAST," Wikipedia, The Free Encyclopedia. [Online]. \\Available: https://en.wikipedia.org/wiki/PSI-BLAST. [Accessed: Feb. 6, 2025].
        \end{latin}

    \bibitem{bib8}
        \begin{latin}
            "Sequence logo," Wikipedia, The Free Encyclopedia. [Online]. \\
            Available: https://en.wikipedia.org/wiki/Sequence\_logo. [Accessed: Feb. 6, 2025].
        \end{latin}

    \bibitem{bib9}
        \begin{latin}
            "Xylanase," Wikipedia, The Free Encyclopedia. [Online]. \\
            Available: https://en.wikipedia.org/wiki/Xylanase. [Accessed: Feb. 6, 2025].
        \end{latin}

    \bibitem{bib10}
        \begin{latin}
            OpenAI, "ChatGPT: Language Model," [Online]. Available: https://chat.openai.com/. [Accessed: Feb. 8, 2025].\footnote{برای دیباگ کردن و یافتن تعدادی از دستورات}
        \end{latin}

    \end{thebibliography}